Astro 507; Problem Set 4

### 2022-03-09 pset4/solutions.tex
pset4 q2c

\question{2c. \textbf{Temperature Assumptions}}
\answer{

>>>>

\question{2c. \textbf{Temperature Assumptions}}
\answer{
    It is a good approximation that there is no temperature dependence in this equation because the degeneracy pressure plays a much more important role at these low temperatures. The water/ice is not changing phase around these temperatures and the microscopic velocities are not very high, thus the effect on the overall pressure/density is comparitvely negigible.
}
